### 2024-03-29 outputs/paper/paper.qmd
clean data script updated, clean data added, paper updated accordingly

# load packages
packages <- c("tidyverse", "boot", "broom.mixed", "collapse", "dataverse", "gutenbergr", "janitor", "knitr", "marginaleffects", "modelsummary", "rstanarm", "tidybayes", "loo")

@@

# read in data
file_path_0 <- "../../inputs/data/raw_data.csv"
file_path_1 <- "../../outputs/data/cleaned_data.csv"
file_path_2 <- "../../outputs/data/top_5_cause_data.csv"
file_path_3 <- "../../outputs/data/summarized_top_5_cause_data.csv"

raw_data <- read_csv(file_path_0, show_col_types = FALSE)
cleaned_data <- read_csv(file_path_1, show_col_types = FALSE)
top_5_cause_data <- read_csv(file_path_2, show_col_types = FALSE)
summarized_top_5_cause_data <- read_csv(file_path_3, show_col_types = FALSE)
```

@@

Data used in this paper was cleaned, processed and tested with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `readr` [@citeReadr], `knitr` [@citeKnitr], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `tidybayes` [@citeTidybayes], `loo` [@citeLoo], `testthat` [@citeTestthat].

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-causes
#| tbl-cap: top 8 major causes in 2019

@@

>>>>

# load packages
packages <- c("tidyverse", "boot", "broom.mixed", "collapse", "dataverse", "gutenbergr", "janitor", "knitr", "marginaleffects", "modelsummary", "rstanarm", "tidybayes", "loo", "kableExtra")

@@

# read in data
file_path_0 <- "../../inputs/data/cali_house_price.csv"
file_path_1 <- "../../outputs/data/cali_house_price_clean.csv"
file_path_2 <- "../../outputs/data/.csv"
file_path_3 <- "../../outputs/data/.csv"

cali_house_price <- read_csv(file_path_0, show_col_types = FALSE)
cali_house_price_clean<- read_csv(file_path_1, show_col_types = FALSE)

@@

Data used in this paper was cleaned, processed and tested with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `readr` [@citeReadr], `knitr` [@citeKnitr], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `tidybayes` [@citeTidybayes], `loo` [@citeLoo], `testthat` [@citeTestthat], `KableExtra` [@citeKableEx].

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-sum
#| tbl-cap: Summary statistics of the California housing dataset
#| layout-ncol: 3
#| layout-nrow: 3

longitude_summary <- summary(cali_house_price %>% select(longitude))
latitude_summary <- summary(cali_house_price %>% select(latitude))
housing_median_age_summary <- summary(cali_house_price %>% select(housing_median_age))
total_rooms_summary <- summary(cali_house_price %>% select(total_rooms))
total_bedrooms_summary <- summary(cali_house_price %>% select(total_bedrooms))
population_summary <- summary(cali_house_price %>% select(population))
households_summary <- summary(cali_house_price %>% select(households))
median_income_summary <- summary(cali_house_price %>% select(median_income))
median_house_value_summary <- summary(cali_house_price %>% select(median_house_value))

kable(longitude_summary)
kable(latitude_summary)
kable(housing_median_age_summary)
kable(total_rooms_summary)
kable(total_bedrooms_summary)
kable(population_summary)
kable(households_summary)
kable(median_income_summary)
kable(median_house_value_summary)

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-null-raw
#| tbl-cap: Count of missing values for each variable

null_values <- cali_house_price %>%
  summarise_all(~sum(is.na(.))) %>%
  gather(key = "Variables", value = "MissingValues")

kable(null_values)
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-null-clean
#| tbl-cap: Count of missing values for each variable after cleaning

null_values <- cali_house_price_clean %>%
  summarise_all(~sum(is.na(.))) %>%
  gather(key = "Variables", value = "MissingValues")

kable(null_values)
```
